---
title: "04 Data Structures"
author: "csiu"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

```
OBJECTIVES
- To be aware of the different types of data.
- To begin exploring data frames, and understand how they are related to vectors, factors and lists.
- To be able to ask questions from R about the type, class, and structure of an object.
```

## Types of data

- 5 main basic types of data
    - double
    - integer
    - complex
    - logical
    - character
- Data structures
    - data frames: think table and each column can be a different basic type
    - vector: ordered list of things
        - `c()` append things to an existing vector
    - factor: look like character data, but are typically used to represent categorical information
        - R has replaced our human-readable categories with numbered indices under the hood
        - default factors are labelled in alphabetical order
    - lists: can put anything in it
    - matrices: table of numbers

- Type coercion
    - when R encounters a mix of types (here numeric and character) to be combined into a single vector, it will force them all to be the same type
    - coercion rules go: logical -> integer -> numeric -> complex -> character

```{r}
# force coercion against the flow with "as." functions
as.numeric(character_vector_example)
as.logical(character_coerced_to_numeric)
```

## Data frames

- Read in data: `read.csv`, `read.delim`, `read.table`
- Pull out columns by `$` 

## Inspecting an object

```{r}
sequence_example <- seq(10)

head(sequence_example, n=2)
tail(sequence_example, n=4)
length(sequence_example)
class(sequence_example)
typeof(sequence_example)
str(sequence_example)
```
